\renewcommand{\baselinestretch}{1}

\begin{thebibliography}{plain}



\bibitem[1]{goodfellow2016deep}
Goodfellow I, Bengio Y, Courville A, et al. Deep learning[M]. Cambridge: MIT press, 2016.

\bibitem[2]{goodfellow2014generative}
Goodfellow I, Pouget-Abadie J, Mirza M, et al. Generative adversarial nets[C]//Advances in neural information processing systems. 2014: 2672-2680.

\bibitem[3]{radford2015unsupervised}
Radford A, Metz L, Chintala S. Unsupervised representation learning with deep convolutional generative adversarial networks[J]. arXiv preprint arXiv:1511.06434, 2015.

\bibitem[4]{arjovsky2017wasserstein}
Arjovsky M, Chintala S, Bottou L. Wasserstein gan[J]. arXiv preprint arXiv:1701.07875, 2017.

\bibitem[5]{gulrajani2017improved}
Gulrajani I, Ahmed F, Arjovsky M, et al. Improved training of wasserstein gans[C]//Advances in Neural Information Processing Systems. 2017: 5769-5779.

\bibitem[6]{zhu2016generative}
Zhu J Y, Krähenbühl P, Shechtman E, et al. Generative visual manipulation on the natural image manifold[C]//European Conference on Computer Vision. Springer, Cham, 2016: 597-613.

\bibitem[7]{emmelmann2011bionic}
Emmelmann C, Petersen M, Kranz J, et al. Bionic lightweight design by laser additive manufacturing (LAM) for aircraft industry[C]//SPIE Eco-Photonics 2011: Sustainable Design, Manufacturing, and Engineering Workforce Education for a Green Future. International Society for Optics and Photonics, 2011, 8065: 80650L.

\bibitem[8]{klahn2014design}
Klahn C, Leutenecker B, Meboldt M. Design for Additive Manufacturing–Supporting the substitution of components in series products[J]. Procedia CIRP, 2014, 21: 138-143.

\bibitem[9]{emmelmann2011laser}
Emmelmann C, Sander P, Kranz J, et al. Laser additive manufacturing and bionics: redefining lightweight design[J]. Physics Procedia, 2011, 12: 364-368.

\bibitem[10]{zhao2011lightweight}
Zhao L, Ma J, Chen W, et al. Lightweight design and verification of gantry machining center crossbeam based on structural bionics[J]. Journal of Bionic Engineering, 2011, 8(2): 201-206.

\bibitem[11]{赵彻2017}
赵彻. 异质材料与微结构耦合仿生设计及其 3D 打印[D]. 吉林大学, 2017.

\bibitem[12]{fratzl2007nature}
Fratzl P, Weinkamer R. Nature’s hierarchical materials[J]. Progress in Materials Science, 2007, 52(8): 1263-1334.

\bibitem[13]{fabritius2009influence}
Fabritius H O, Sachs C, Triguero P R, et al. Influence of Structural Principles on the Mechanics of a Biological Fiber‐Based Composite Material with Hierarchical Organization: The Exoskeleton of the Lobster Homarus americanus[J]. Advanced materials, 2009, 21(4): 391-400.

\bibitem[14]{da2015plant}
da Silva N R, Florindo J B, Gómez M C, et al. Plant identification based on leaf midrib cross-section images using fractal descriptors[J]. PloS one, 2015, 10(6): e0130014.

\bibitem[15]{ma2008elastic}
Ma J, Chen W, Zhao L, et al. Elastic buckling of bionic cylindrical shells based on bamboo[J]. Journal of Bionic Engineering, 2008, 5(3): 231-238.

\bibitem[16]{maier2013transfer}
Maier M, Siegel D, Thoben K D, et al. Transfer of natural micro structures to bionic lightweight design proposals[J]. Journal of Bionic Engineering, 2013, 10(4): 469-478.

\bibitem[17]{dalal2005histograms}
Dalal N, Triggs B. Histograms of oriented gradients for human detection[C]//Computer Vision and Pattern Recognition, 2005. CVPR 2005. IEEE Computer Society Conference on. IEEE, 2005, 1: 886-893.

\end{thebibliography}
